%-----------------------------------------------------
% index key words
%-----------------------------------------------------
\index{row equivalent}
\index{matrix!row equivalent}

%-----------------------------------------------------
% name, leave blank
% title, if the exercise has a name i.e. Hilbert's matrix
% difficulty = n, where n is the number of stars
% origin = "\cite{ref}"
%-----------------------------------------------------
\begin{Exercise}[
name={},
title={}, 
difficulty=0,
origin={\cite{BS, YL}}]
Determine whether the following statement is true or false for any $n\times n$
matrices $A$ and $B$.  If the statement is false provide a counterexample. If the
statement is true provide a proof of the statement.\\

\Question If $A$ and $B$ are invertible then $A$ and $B$ are row equivalent.
\Question All elementary matrices are symmetric.
\Question If $A$ is elementary then $A^2$ is elementary.
\Question If $A^2$ is an elementary matrix then $A$ is an elementary matrix.
\end{Exercise}

\begin{Answer}
\Question True, the reduced row echelon form of $A$ and $B$ is $I$ since both matrices are invertible.  Hence there exists a finite sequence of elementary row operations that when applied on $A$ result in $I$. And a second finite sequence of elementary row operations that when applied on $B$ result in $I$.  If the first sequence of elementary row operations is applied on $A$ followed by the inverse elementary row operations applied in reverse order of the second sequence of elemtary row operations then $B$ is obtained.  Hence $A$ and $B$ are row equivalent.
\Question False, $\begin{mat}1 & 2\\0 & 1\end{mat}$ is elementary but not symmetric.
\Question True, show that for each type of elementary matrices they are still elementary when squared.
\Question False, if $A=\begin{mat}-1 & 0\\ 0 & -1\end{mat}$ then $A^2=I$ which is an elementary matrix but $A$ is not an elementary matrix.
\end{Answer}
