%-----------------------------------------------------
% index key words
%-----------------------------------------------------
\index{linear independence}
\index{linear dependence}
\index{function space}

%-----------------------------------------------------
% name, leave blank
% title, if the exercise has a name i.e. Hilbert's matrix
% difficulty = n, where n is the number of stars
% origin = "\cite{ref}"
%-----------------------------------------------------
\begin{Exercise}[
name={},
title={}, 
difficulty=0,
origin={\cite{JH}}]
    Which of these subsets of the space of real-valued functions
    of one real variable are linearly dependent and which are linearly
    independent?
\begin{multicols}{2}
\Question \( \set{2,\;4\sin^2(x),\;\cos^2(x)} \)
\Question \( \set{1,\;\sin(x),\;\sin(2x)} \)
\Question \( \set{x,\;\cos(x)} \)
\Question \( \set{(1+x)^2,\;x^2+2x,\;3} \)
\Question \( \set{0,\;x,\;x^2} \)
\Question \( \set{\cos(2x),\;\sin^2(x),\;\cos^2(x)} \)
\EndCurrentQuestion
\end{multicols}
\end{Exercise}

\begin{Answer}
        \Question This set is dependent.
          The familiar relation $\sin^2(x)+\cos^2(x)=1$ shows that
          $2=c_1\cdot(4\sin^2(x))+c_2\cdot(\cos^2(x))$ is satisfied by
          $c_1=1/2$ and $c_2=2$.
        \Question This set is independent.
          Consider the relationship
          $c_1\cdot 1+c_2\cdot\sin(x)+c_3\cdot\sin(2x)=0$
          (that `$0$' is the zero function).
          Taking three suitable points such as $x=\pi$, $x=\pi/2$, $x=\pi/4$ 
          gives a system
          \begin{equation*}
            \begin{linsys}{3}
               c_1  &   &                &   &      &=  &0  \\
               c_1  &+  &c_2             &   &      &=  &0  \\
               c_1  &+  &(\sqrt{2}/2)c_2 &+  &c_3   &=  &0  
            \end{linsys}
          \end{equation*}
          whose only solution is 
          $c_1=0$, $c_2=0$, and $c_3=0$. 
        \Question By inspection, this set is independent.
          Any dependence $\cos(x)=c\cdot x$ is not possible since the cosine
          function is not a multiple of the identity function
        \Question By inspection, we spot that there is a dependence.
          Because $(1+x)^2=x^2+2x+1$, we get that
          $c_1\cdot(1+x)^2+c_2\cdot(x^2+2x)=3$ is satisfied by 
          $c_1=3$ and $c_2=-3$.
	\Question This set is dependent, because it contains the
          zero object in the vector space, the zero polynomial.
        \Question This set is dependent.
          The easiest way to see that is to recall the trigonometric
          relationship $\cos^2(x)-\sin^2(x)=\cos(2x)$.

\end{Answer}
